The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-02 outputs/paper/paper.Rmd
ggplot

@@

urban_rural <- pivot_longer(data[1:2, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
region <- pivot_longer(data[3:7, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
education <- pivot_longer(data[8:11, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
religion <- pivot_longer(data[12:13, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
population <- data.frame(Variable = data$Variable, 
                         Population = data$Number_of_Children) %>% head(-1)
population$Variable <- factor(population$Variable,
                              levels = population$Variable) %>% fct_rev()
```

```{r}

# create new dataset only for urban-rural data
# urban_rural <- data.frame(location = c(rep("urban", data[1,6]), rep("rural", data[2,6])),
#                 immune_data =  c(rep("Health Report", round(data[1,2]*data[1,6]/100)), rep("Mothers Report", round(data[1,3]*data[1,6]/100)), rep("No immune", round(data[1,5]*data[1,6]/100)), 
#                                  rep("Health Report", round(data[2,2]*data[2,6]/100)), rep("Mothers Report", round(data[2,3]*data[2,6]/100)), rep("No immune", round(data[2,5]*data[2,6]/100)))
#                 
#                 )

# create new dataset only for for region
# region <- data.frame(region = c(rep("north", data[3,6]), rep("north_east", data[4,6]), rep("central", data[5,6]), rep("south", data[6,6]), rep("bangkok", data[7,6])),
#                     immune_data =  c(rep("Health Report", round(data[3,2]*data[3,6]/100)), rep("Mothers Report", round(data[3,3]*data[3,6]/100)), rep("No immune", round(data[3,5]*data[3,6]/100)), 
#                                  rep("Health Report", round(data[4,2]*data[4,6]/100)), rep("Mothers Report", round(data[4,3]*data[4,6]/100)), rep("No immune", round(data[4,5]*data[4,6]/100)),
#                                  rep("Health Report", round(data[5,2]*data[5,6]/100)), rep("Mothers Report", round(data[5,3]*data[5,6]/100)), rep("No immune", round(data[5,5]*data[5,6]/100)), 
#                                  rep("Health Report", round(data[6,2]*data[6,6]/100)), rep("Mothers Report", round(data[6,3]*data[6,6]/100)), rep("No immune", round(data[6,5]*data[6,6]/100)),
#                                  rep("Health Report", round(data[7,2]*data[7,6]/100)), rep("Mothers Report", round(data[7,3]*data[7,6]/100)), rep("No immune", round(data[7,5]*data[7,6]/100)))
#                     )

# create new dataset only for for education. due to an error in the dataset provided by DHS, some rows will be filled with NA.

 # no_edu <-data.frame(education = c(rep("no_edu", 265)),
 #                     immune_data = c(rep("Health Report", round(data[8,2]*data[8,6]/100)), rep("Mothers Report", round(data[8,3]*data[8,6]/100)), rep("No immune", round(data[8,5]*data[8,6]/100)))
 #                     )
 # 
 # primary <-data.frame(education = c(rep("primary", data[9,6])),
 #                     immune_data = c(rep("Health Report", round(data[9,2]*data[9,6]/100)), rep("Mothers Report", floor(data[9,3]*data[9,6]/100)), rep("No immune", round(data[9,5]*data[9,6]/100)))
 #                     )
 # 
 # secondary <-data.frame(education = c(rep("secondary", data[10,6])),
 #                     immune_data = c(rep("Health Report", floor(data[10,2]*data[10,6]/100)), rep("Mothers Report", floor(data[10,3]*data[10,6]/100)), rep("No immune", round(data[10,5]*data[10,6]/100)))
 #                    )
# education <- data.frame(education = c(rep("no_education", round(data[8,2]*data[8,6]/100) + round(data[8,3]*data[8,6]/100) + round(data[8,5]*data[8,6]/100)), 
#                                       rep("primary", round(data[9,2]*data[9,6]/100) + round(data[9,3]*data[9,6]/100) + round(data[9,5]*data[9,6]/100)), 
#                                       rep("secondary", round(data[10,2]*data[10,6]/100) + round(data[10,3]*data[10,6]/100) + round(data[10,5]*data[10,6]/100)),
#                                       rep("higher", round(data[11,2]*data[11,6]/100) + round(data[11,3]*data[11,6]/100) + round(data[11,5]*data[11,6]/100))),
#                     immune_data =  c(rep("Health Report", round(data[8,2]*data[8,6]/100)), rep("Mothers Report", round(data[8,3]*data[8,6]/100)), rep("No immune", round(data[8,5]*data[8,6]/100)),
#                                  rep("Health Report", round(data[9,2]*data[9,6]/100)), rep("Mothers Report", round(data[9,3]*data[9,6]/100)), rep("No immune", round(data[9,5]*data[9,6]/100)),
#                                  rep("Health Report", round(data[10,2]*data[10,6]/100)), rep("Mothers Report", round(data[10,3]*data[10,6]/100)), rep("No immune", round(data[10,5]*data[10,6]/100)),
#                                  rep("Health Report", round(data[11,2]*data[11,6]/100)), rep("Mothers Report", round(data[11,3]*data[11,6]/100)), rep("No immune", round(data[11,5]*data[11,6]/100)))
#                     )

# create new dataset only for for education
# religion <- data.frame(religion = c(rep("Buddhist", data[12,6]), rep("Islam", data[13,6])),
#                 immune_data =  c(rep("Health Report", round(data[12,2]*data[12,6]/100)), rep("Mothers Report", round(data[12,3]*data[12,6]/100)), rep("No immune", round(data[12,5]*data[12,6]/100)), 
#                                  rep("Health Report", round(data[13,2]*data[13,6]/100)), rep("Mothers Report", round(data[13,3]*data[13,6]/100)), rep("No immune", round(data[13,5]*data[13,6]/100)))
#                       )
# 
# total <- data.frame(total = c(rep("total", data[14,6])),
#                 immune_data =  c(rep("Health Report", floor(data[14,2]*data[14,6]/100)), rep("Mothers Report", floor(data[14,3]*data[14,6]/100)), rep("No immune", floor(data[14,5]*data[14,6]/100)))
#                       )
```

```{r fig1,echo=FALSE, fig.cap = "Immunization cases between variables"}
population %>%
  ggplot(aes(x = Variable, y = Population, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

```{r fig2,echo=FALSE, fig.cap = "Immunization cases between communities"}
#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
urban_rural %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

```{r fig3,echo=FALSE, fig.cap = "Immunization cases between region"}
#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
region %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r fig4,echo=FALSE, fig.cap = "Immunization cases between education"}
#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
education %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

```{r fig5,echo=FALSE, fig.cap = "Immunization cases between religion"}
#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
religion %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

```{r fig6,echo=FALSE, fig.cap = "Immunization and non-immunization cases total"}
total %>%
  ggplot(aes(x = immune_status, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

>>>>

This report was created using `R` [@citeR] and its libraries `tidyverse` [@tidyverse], `dplyr` [@dplyr], were used to process and clean the data, and `ggplot` [@ggplot] `bookdown` [@bookdown] and `knitr` [@knitr] was used to format this report.

@@

urban_rural <- pivot_longer(data[1:2, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
region <- pivot_longer(data[3:7, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
education <- pivot_longer(data[8:11, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
religion <- pivot_longer(data[12:13, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
population <- data.frame(group = c(rep("urban-rural", 2), rep("region", 5), rep("education", 4), rep("religion", 3)),
                                           Variable = data$Variable, 
                         Population = data$Number_of_Children) %>% head(-1)
population$Variable <- factor(population$Variable,
                              levels = population$Variable) %>% fct_rev()
```

```{r fig1,echo=FALSE, fig.cap = "Number of children by category"}
population %>%
  ggplot(aes(x = Variable, y = Population, fill = group)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()  +
  labs(x = element_blank(),
       y = "Population",
       title = "Distribution of Population of Children by Category",
       ) +
  facet_grid(group ~ ., scales="free", space="free", switch="y") +
  theme(legend.title = element_blank()) +
  theme(legend.position = "none")
```

```{r fig2,echo=FALSE, fig.cap = "Immunization cases between communities"}
#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
urban_rural %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()  +
  labs(x = element_blank(),
       y = "Percent",
       title = "Percentage of Children's Immunization Status by Urban-Rural Area",
       ) +
  theme(legend.title = element_blank())
```

```{r fig3,echo=FALSE, fig.cap = "Immunization cases between region"}
#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
region %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()  +
  labs(x = element_blank(),
       y = "Percent",
       title = "Percentage of Children's Immunization Status by Region",
       ) +
  theme(legend.title = element_blank())
```
```{r fig4,echo=FALSE, fig.cap = "Immunization cases between education"}
#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
education %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()  +
  labs(x = element_blank(),
       y = "Percent",
       title = "Percentage of Children's Immunization Status by Education",
       ) +
  theme(legend.title = element_blank())
```

```{r fig5,echo=FALSE, fig.cap = "Immunization cases between religion"}
#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
religion %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()  +
  labs(x = element_blank(),
       y = "Percent",
       title = "Percentage of Children's Immunization Status by Religion",
       ) +
  theme(legend.title = element_blank())
```

```{r fig6,echo=FALSE, fig.cap = "Immunization and non-immunization cases total"}
total %>%
  ggplot(aes(x = immune_status, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip() +
  labs(x = element_blank(),
       y = "Percent",
       title = "Total Percentage of Children's Immunization Status",
       ) +
  theme(legend.position = "none")
```
